---
title: "P8105_hw1_qh2251"
author: "Paulina Han"
date: "2021/9/23"
output: github_document
---

```{r,echo = FALSE, message = FALSE}
library(tidyverse)
```

# Problem 1
```{r}
set.seed(12)

df_1 = tibble(
  vec_numeric = rnorm(10),
  vec_logical = vec_numeric>0,
  vec_char = c("a", "b", "c", "d","e","f","g","h","i","j"),
  vec_factor = factor(c("blue","blue","blue","red","red","red","yellow","yellow","yellow","yellow"))
  )

mean(pull(df_1,vec_numeric))
mean(pull(df_1,vec_logical))
mean(pull(df_1,vec_char))
mean(pull(df_1,vec_factor))
```

The numerical and logical vectors work,but the character and factor vectors don't work.

```{r,eval = FALSE}
mean(as.numeric(pull(df_1,vec_logical)))
mean(as.numeric(pull(df_1,vec_char)))
mean(as.numeric(pull(df_1,vec_factor)))

```
the `mean` function works for the converted logical vector and the converted factor vector.However the `mean` function doesn't work for the converted character vector.

the `as.numeric` function set TRUE to 1 and FALSE to 0 for the logical vector.the `as.numeric` function set "blue" to 1,"red" to 2,"yellow" to 3 for the factor vector. In this way the `mean` function works. All characters were converted to NA by `as.numeric` function so it won't work for the `mean` function.

So when you try to take the mean of a vector , you have to make sure it is a numerical vector.logical vectors can be treated as numerical vectors by default of `mean`function.

# Problem 2
```{r}
library(palmerpenguins)

#load the data from the package
data("penguins", package = "palmerpenguins")

#name and important values of the data

#species
Adelie = sum(pull(penguins,species) == 'Adelie')
Chinstrap = sum(pull(penguins,species) == 'Chinstrap')
Gentoo = sum(pull(penguins,species) == 'Gentoo')
#body_mass
na = sum(is.na(pull(penguins,body_mass_g)))
body_mass_mean = mean(pull(penguins,body_mass_g))
body_mass_min = min(pull(penguins,body_mass_g))
body_mass_max = max(pull(penguins,body_mass_g))

#flipper_length
na_flipper = sum(is.na(pull(penguins,flipper_length_mm)))
flipper_length_mm_mean = mean(pull(penguins,flipper_length_mm),na.rm = T)
flipper_length_mm_min = min(pull(penguins,flipper_length_mm),na.rm = T)
flipper_length_mm_max = max(pull(penguins,flipper_length_mm),na.rm = T)

#size of the data set
row = nrow(penguins)
col = ncol(penguins)

#mean flipper length(removing all NAs)
mean=mean(pull(penguins,flipper_length_mm),na.rm = TRUE)

```

The species is a factor variable which has `r Adelie` Adelie penguins, `r Chinstrap` Chinstrap penguins and `r Gentoo` Gentoo penguins.

The body_mass_g is a numeric variable with `r na` missing values. The mean is `r body_mass_mean`, the minimum is `r body_mass_min`, the maximum is `r body_mass_max`.

The flipper_length_mm is a numeric variable with `r na_flipper` missing values. The mean is `r flipper_length_mm_mean` , the minimum is `r flipper_length_mm_min`, the maximum is `r flipper_length_mm_max` .


There are `r row` rows and  `r col` columns in the data set.

The mean flipper length is`r mean`.


```{r}
#drawing a  plot
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species )) + geom_point()

#save the plot
ggsave("scatter_plot.pdf", height = 4, width = 6)

```




